Log or not

### 2021-10-25 analysis/Analysis.Rmd
restructure plots

grid_sigma_mult <- seq(0.5, 2.5, by = 0.1)
grid_mu_mult <- seq(0.5, 2.5, by = 0.1)
grid_sigma_add <- seq(0, 100, by = 5)
grid_mu_add <- seq(0, 1000, by = 50)

@@

# helper function to plot scores
plot_scores <- function(scores) {
  scores |>
    mutate("True parameters" = 
             paste0("mean: ", mu_true, ", sd: ", sigma_true)) |>
    group_by(`True parameters`, error, scale) |>
    summarise(interval_score = mean(interval_score)) |>
    ggplot(aes(x = error, y = interval_score, 
               colour = `True parameters`, group = `True parameters`)) + 
    geom_line() + 
    scale_color_brewer(palette = "Set1", name = "True parameters: ") + 
    facet_wrap(~ scale, scale = "free") + 
    theme_minimal() + 
    theme(legend.position = "bottom") 
}

@@

```{r eval = rerun_simulation}
for (i in 1:nrow(scenarios)) {
  equal_mean <- scenarios[i, ]$truth_mean_equal
  equal_var <- scenarios[i, ]$truth_var_equal
  grid <- unlist(scenarios[i, ]$grid)
  error_var <- scenarios[i, ]$error_var
  error_type <- scenarios[i, ]$error_type
  scenario_name <- scenarios[i, ]$name
  scenario_title <- scenarios[i, ]$title

@@

  joined_scores <- join_scores(scores_1, scores_2)
  joined_log_scores <- join_scores(log_scores_1, log_scores_2, scale = "log")
  combined_scores <- rbind(joined_scores, joined_log_scores)

  plot_scores(combined_scores) + 
    ggtitle(wrap_title(scenario_title, width = 60)) + 
    labs(y = "Interval Score", 
         x = paste(error_type, "error on", error_var) |> 
           str_to_sentence())

@@

>>>>

grid_sigma_mult <- seq(0.5, 2, by = 0.1)
grid_mu_mult <- seq(0.5, 2, by = 0.1)
grid_sigma_add <- seq(-5, 10, by = 1)
grid_mu_add <- seq(-500, 1000, by = 100)

@@

# helper function to plot scores
plot_scores <- function(scores) {
  scores |>
    mutate("True parameters" = 
             paste0("mean: ", mu_true, ", sd: ", sigma_true)) |>
    group_by(`True parameters`, error, scale) |>
    summarise(interval_score = mean(interval_score)) |>
    group_by(scale) |>
    mutate(multplicative_score = interval_score / min(interval_score)) |>
    ggplot(aes(x = error, y = multplicative_score, 
               colour = `True parameters`, group = `True parameters`)) + 
    geom_line() + 
    scale_color_brewer(palette = "Set1", name = "True parameters: ") + 
    scale_y_continuous(limits = c(1, NA), expand = c(1, NA)) + 
    expand_limits(y = c(1, NA)) + 
    facet_wrap(~ scale, scale = "free") + 
    theme_minimal() + 
    theme(legend.position = "bottom") 
}

@@

```{r eval = rerun_simulation}

results <- list()

for (i in 1:nrow(scenarios)) {
  equal_mean <- scenarios[i, ]$truth_mean_equal
  equal_var <- scenarios[i, ]$truth_var_equal
  grid <- unlist(scenarios[i, ]$grid)
  error_var <- scenarios[i, ]$error_var
  error_type <- scenarios[i, ]$error_type
  scenario_name <- scenarios[i, ]$name
  scenario_title <- scenarios[i, ]$title

@@

  joined_scores <- join_scores(scores_1, scores_2)
  joined_log_scores <- join_scores(log_scores_1, log_scores_2, scale = "log")
  combined_scores <- rbind(joined_scores, joined_log_scores) |>
    mutate(equal_mean = equal_mean, 
           equal_var = equal_var)

  # store all results
  results[[scenario_name]] <- combined_scores

  plot_scores(combined_scores) + 
    ggtitle(wrap_title(scenario_title, width = 60)) + 
    labs(y = "Multiplicative change in Interval Score", 
         x = paste(error_type, "error on", error_var) |> 
           str_to_sentence())

@@

```{r}
results

res <- bind_rows(results)

plot_multiple <- function(res, equal_means, equal_vars) {
  res <- res |>
    filter(equal_mean == equal_means, 
           equal_var == equal_vars) |>
    mutate("True parameters" = 
             paste0("mean: ", mu_true, ", sd: ", sigma_true)) |>
    group_by(`True parameters`, error, error_type, error_var, scale) |>
    summarise(interval_score = mean(interval_score)) |>
    group_by(scale, error_var, error_type) |>
    mutate(multplicative_score = interval_score / min(interval_score), 
           error_title = str_to_title(
             paste(error_type, "on", error_var)))

  res |> 
    ggplot(aes(x = error, y = multplicative_score, 
               colour = `True parameters`, group = `True parameters`)) + 
    geom_line() + 
    scale_color_brewer(palette = "Set1", name = "True parameters: ") + 
    # scale_y_continuous(limits = c(1, NA), expand = c(0, NA)) + 
    expand_limits(y = c(1, NA)) + 
    facet_wrap( ~ error_title + scale, scale = "free", nrow = 2) + 
    theme_minimal() + 
    theme(legend.position = "bottom") +
    labs(y = "Multiplicative change in Interval Score", 
         x = "Error") + 
    geom_rect(data = subset(res, error_var == "sigma"), 
              fill = NA, colour = "grey80", xmin = -Inf,xmax = Inf,
              ymin = -Inf,ymax = Inf) + 
    geom_rect(data = subset(res, error_var == "mu"), 
              fill = NA, colour = "grey70", xmin = -Inf,xmax = Inf,
              ymin = -Inf,ymax = Inf) 
}
```

```{r}
p1 <- plot_multiple(res, equal_means = TRUE, equal_vars = TRUE) 
ggsave(p1, filename = here("output", "effect_equal_mean_equal_var.png"))

p1 + 
  ggtitle("Effect of scoring on a log scale")
```

```{r}
p2 <- plot_multiple(res, equal_means = FALSE, equal_vars = TRUE) 
ggsave(p2, filename = here("output", "effect_unequal_mean_equal_var.png"))

p2 + 
  ggtitle("Effect of scoring on a log scale for two variables with unequal means")
```

```{r}
p3 <- plot_multiple(res, equal_means = TRUE, equal_vars = FALSE) 
ggsave(p3, filename = here("output", "effect_equal_mean_unequal_var.png"))

p3 + 
  ggtitle("Effect of scoring on a log scale for two variables with unequal variances")
```

```{r}
p4 <- plot_multiple(res, equal_means = FALSE, equal_vars = FALSE) 
ggsave(p4, filename = here("output", "effect_unequal_mean_unequal_var.png"))

title <- "Effect of scoring on a log scale for two variables with unequal means and unequal variances"
p4 + 
  ggtitle(wrap_title(title, width = 80))
```
